---
title: "RWorksheet_Bajacan#3b"
author: "Gilbert Bajacan"
output: pdf_document
date: "2023-10-10"
---

#NUMBER 1
#A.
``` {r number1a}
household <- data.frame (
  Respondents = 1:20, 
  Sex = c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2), 
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1), 
  Person_at_Home = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6),
  Siblings_at_school = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
  Types_of_houses = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)
)
household
```
#B.
``` {r number1b}
str(household)
summary(household)
```

#C.
``` {r number1c}
mean_siblings <- mean(household$Siblings_at_school)
mean_siblings == 5
```

#D.
``` {r number1d}
subset1 <- household[1:2, ]
subset1
```

#E.
``` {r number1e}
subset2 <- household[c(3, 5), c(2, 4)]
subset2
```
#F.
``` {r number1f}
types_houses <- household$Types_of_houses
types_houses
```
#G.
``` {r number1g}
male_farmer <- subset(household, Sex == 1 & Fathers_Occupation == 1)
male_farmer
```

#H.
``` {r number1h}
female_greater_than_5_siblings <- subset(household, Sex == 2 & Siblings_at_school >= 5)
female_greater_than_5_siblings
```

#NUMBER 2
``` {r number2} 
df <- data.frame(
  Ints = integer(),
  Doubles = double(),
  Characters = character(),
  Logicals = logical(),
  Factors = factor(),
  stringsAsFactors = FALSE
)
cat("Structure of the empty dataframe:\n")
str(df)
```
#Output
The output shows that the data frame has 0 observations (rows) and 5 variables (columns) with their respective data types. The "Factors" column is empty since there are no levels defined yet.

#NUMBER 3
``` {r number3}
household_data <- data.frame (
  Respondents = 1:10, 
  Sex = c("Male", "Female", "Female", "Male", "Male", "Female", "Female", "Male", "Female", "Male"), 
  Fathers_Occupation = c(1,2,3,3,1,2,2,3,1,3), 
  Person_at_Home = c(5,7,3,8,6,4,4,2,11,6),
  Siblings_at_school = c(2,3,0,5,2,3,1,2,6,2),
  Types_of_houses = c("Wood", "Congrete", "Congrete", "Wood", "Semi-Congrete", "Semi-Congrete", "Wood", "Semi-Congrete", "Semi-Congrete", "Congrete")
)
household_data
write.csv(household_data, file = "HouseholdData.csv", row.names = FALSE)
```
#A.
``` {r number3a}
household_data <- read.csv("HouseholdData.csv")
```
#B.
``` {r number3b}
household_data$Sex <- factor(household_data$Sex)
household_data$Sex <- as.integer(factor(household_data$Sex, 
                                 levels = c("Male", "Female"),
                                    labels = c(1, 2)))
household_data
```
#C.
``` {r number3c}
household_data$Types_of_houses <- factor(household_data$Types_of_houses)
household_data$Types_of_houses <- as.integer(factor(household_data$Types_of_houses,
                                              levels = c("Wood", "Congrete", "Semi-Congrete"),
                                                    labels = c(1, 2, 3)))
print(household_data)
```

#D.
``` {r number3d}
household_data$Fathers_Occupation <- factor(household_data$Fathers_Occupation)
household_data$Fathers_Occupation <- as.character(factor(household_data$Fathers_Occupation,
                                            
                                            levels = c(1, 2, 3),
                                            labels = c("Farmer", "Driver", "Others")))

# Print the updated data frame
print(household_data)


```

#E.
``` {r number3e}
female_driver <- subset(household_data, Sex == 2 & Fathers_Occupation == "Driver")
female_driver
```

#F.
``` {r number3f}
greater_than_5_siblings <- subset(household_data, Siblings_at_school >= 5)
greater_than_5_siblings
```

#4.Interpret Graph
The graph you've provided illustrates sentiment trends on Twitter for the dates July 14, 15, 17, 18, 20, and 21 in the year 2020. Sentiment analysis classifies tweets into three categories: negative, neutral, and positive. Here's an overview of the data:

- July 14, 2020:
  - Negative tweets: Nearly 2,500
  - Neutral tweets: About 1,500
  - Positive tweets: Approximately 1,750

- July 15, 2020:
  - Negative tweets: Over 4,000
  - Neutral tweets: About 2,750
  - Positive tweets: Roughly 3,200

- July 17, 2020:
  - Negative tweets: Approximately 3,250
  - Neutral tweets: Around 1,800
  - Positive tweets: Almost 2,500

- July 18, 2020:
  - Negative tweets: Still around 3,250
  - Neutral tweets: About 2,000
  - Positive tweets: Approximately 2,500

- July 20, 2020:
  - Negative tweets: Nearly 2,500
  - Neutral tweets: About 1,500
  - Positive tweets: Almost 1,750

- July 21, 2020:
  - Negative tweets: Around 4,000
  - Neutral tweets: About 2,600
  - Positive tweets: Roughly 3,300

This data reveals fluctuations in sentiment during the specified dates. July 15th and July 21st stand out with higher numbers of both negative and positive tweets, suggesting increased sentiment-related Twitter activity on those days. Conversely, July 14th and July 20th had lower counts in all sentiment categories. Overall, the data indicates a variable sentiment landscape on Twitter during this period in 2020.s
